---
title: "Events2move behavioral - Experiment 1"
author: "Anna Ivanova"
date: "6/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list=ls()) 

library(lmerTest)
library(ggplot2)
library(dplyr)
library(stringr)
```

## Load behavioral data

```{r load data, echo=FALSE}
files = list.files(path='../data/behavioral/Events2move', pattern="*.csv")
dat = do.call(rbind, lapply(files, function(x) read.csv(paste('../data/behavioral/Events2move/', x, sep=''))))

# clean
dat = dat %>%
  rename(SubjID=subjid, Condition=condition, ItemNum=item,
         Response=response, Accuracy=accuracy) %>%
  mutate(SubjID=str_trim(SubjID, side="both")) %>%
  mutate(Condition = recode(Condition,
                            'Sem-photo'='Pic_Sem',
                            'Sem-sent'='Sent_Sem',
                            'Perc-photo'='Pic_Perc',
                            'Perc-sent'='Sent_Perc'))

# keep only data from participants who also have fMRI results (aka were not excluded)
sessions_clean = read.csv('../Participant_info/TripleEvents_sessions_clean.csv')
sessions_clean_list = as.character(unlist(sessions_clean %>% select(-UID)))
dat = dat %>% filter(SubjID %in% sessions_clean_list)

dat_RT = dat %>%
  filter(!is.na(Response))
dat_acc = dat %>%
    filter(!is.na(Response))
```

## Response Rate

```{r response rate, echo=FALSE}
dat_responserate = dat %>%
  mutate(Responded = ifelse(is.na(RT), 0, 1)) %>%
  group_by(SubjID, Condition) %>%
  summarize(ResponseRate = sum(Responded)/n())

mean_rr = dat_responserate %>%
  group_by(Condition) %>%
  summarize(ResponseRate = mean(ResponseRate))
grandmean_rr = mean(mean_rr$ResponseRate)
mean_rr
```

Average response rate was `r round(grandmean_rr,2)`.

## Reaction Times

```{r RT analysis, echo=FALSE}
dat_sentsem = dat_RT %>% filter(Condition=='Sent_Sem')
cat('Sent Sem RT =', round(mean(dat_sentsem$RT),3), '(SD = ', round(sd(dat_sentsem$RT),3), ')\n')

dat_sentperc = dat_RT %>% filter(Condition=='Sent_Perc')
cat('Sent Perc RT =', round(mean(dat_sentperc$RT),3), '(SD = ', round(sd(dat_sentperc$RT),3), ')\n')

dat_picsem = dat_RT %>% filter(Condition=='Pic_Sem')
cat('Pic Sem RT =', round(mean(dat_picsem$RT),3), '(SD = ', round(sd(dat_picsem$RT),3), ')\n')

dat_picperc = dat_RT %>% filter(Condition=='Pic_Perc')
cat('Pic Perc RT =', round(mean(dat_picperc$RT),3), '(SD = ', round(sd(dat_picperc$RT),3), ')\n')

cat('Overall=', round(mean(dat_RT$RT),3), '(SD = ', round(sd(dat_RT$RT),3), ')\n')
```

Overall reaction time was `r round(mean(dat_RT$RT),2)`s, SD=`r round(sd(dat_RT$RT),2)` 
(Sent Sem: `r round(mean(dat_sentsem$RT),2)`s, SD=`r round(sd(dat_sentsem$RT),2)`; Sent Perc: `r round(mean(dat_sentperc$RT),2)`s, SD=`r round(sd(dat_sentperc$RT),2)`, 
Pic Sem: `r round(mean(dat_picsem$RT),2)`s, SD=`r round(sd(dat_picsem$RT),2)`, Pic Perc: `r round(mean(dat_picperc$RT),2)`s, SD=`r round(sd(dat_picperc$RT),2)`)


```{r lmer model RT, echo=FALSE}
dat_RT = dat_RT %>%
  mutate(StimType = factor(ifelse(Condition %in% c('Sent_Sem', 'Sent_Perc'), 'Sent', 'Pic'),
         levels=c('Pic', 'Sent'))) %>%
  mutate(Task = factor(ifelse(Condition %in% c('Sent_Sem', 'Pic_Sem'), 'Sem', 'Perc'),
         levels=c('Perc', 'Sem')))

contrasts(dat_RT$StimType) = c(-0.5, 0.5)
contrasts(dat_RT$Task) = c(-0.5, 0.5)
colnames(attr(dat_RT$StimType, "contrasts")) = "Sent>Pic"
colnames(attr(dat_RT$Task, "contrasts")) = "Sem>Perc"

m = lmer(RT ~ StimType*Task + (1|SubjID) + (1|ItemNum), data=dat_RT, REML=FALSE)
summary(m)
```

RTs for the semantic task were slightly lower than for the perceptual task ($\beta$=`r round(coef(summary(m))[3,1], 2)`, SE=`r round(coef(summary(m))[3,2], 2)`, p<.001), 
with an interaction between stimulus type and task ($\beta$=`r round(coef(summary(m))[4,1], 2)`, SE=`r round(coef(summary(m))[4,2], 2)`, p=`r round(coef(summary(m))[4,5], 3)`). There was no main effect of stimulus type.


```{r RT plot, echo=FALSE}
ggplot(data=dat_RT %>% filter(RT>0))+
    stat_summary(mapping = aes(x = Condition, y = RT), 
               geom = 'col', fun.y = 'mean', color = 'gray',
               show.legend=FALSE)+
    stat_summary(mapping = aes(x = Condition, y = RT), 
               geom = 'errorbar', fun.data = 'mean_se', color = 'black', 
               size = 1, width=0.3) + theme_minimal()
```

## Accuracies

```{r accuracy analysis, echo=FALSE}
cat('SentSem Accuracy=', mean(dat_sentsem$Accuracy), '\n')
cat('SentPerc Accuracy=', mean(dat_sentperc$Accuracy), '\n')
cat('PicSem Accuracy=', mean(dat_picsem$Accuracy), '\n')
cat('PicPerc Accuracy=', mean(dat_picperc$Accuracy), '\n')
cat('Overall Accuracy=', mean(dat_acc$Accuracy), '\n')
```

Overall mean accuracy was `r round(mean(dat_acc$Accuracy),2)`, SD=`r round(sd(dat_acc$Accuracy),2)` 
(Sent Sem: `r round(mean(dat_sentsem$Accuracy),2)`, SD=`r round(sd(dat_sentsem$Accuracy),2)`; Sent Perc: `r round(mean(dat_sentperc$Accuracy),2)`, SD=`r round(sd(dat_sentperc$Accuracy),2)`, 
Pic Sem: `r round(mean(dat_picsem$Accuracy),2)`, SD=`r round(sd(dat_picsem$Accuracy),2)`, Pic Perc: `r round(mean(dat_picperc$Accuracy),2)`, SD=`r round(sd(dat_picperc$Accuracy),2)`)

```{r acc by person, echo=FALSE}
acc_by_person = dat_acc %>% group_by(SubjID) %>%
  summarize(Accuracy=mean(Accuracy))
```

```{r lmer model accuracy, echo=FALSE}
dat_acc = dat_acc %>%
  mutate(StimType = factor(ifelse(Condition %in% c('Sent_Sem', 'Sent_Perc'), 'Sent', 'Pic'),
         levels=c('Pic', 'Sent'))) %>%
  mutate(Task = factor(ifelse(Condition %in% c('Sent_Sem', 'Pic_Sem'), 'Sem', 'Perc'),
         levels=c('Perc', 'Sem')))

contrasts(dat_acc$StimType) = c(-0.5, 0.5)
contrasts(dat_acc$Task) = c(-0.5, 0.5)
colnames(attr(dat_acc$StimType, "contrasts")) = "Sent>Pic"
colnames(attr(dat_acc$Task, "contrasts")) = "Sem>Perc"

m = glmer(Accuracy ~ StimType*Task + (1|SubjID) + (1|ItemNum), data=dat_RT, family='binomial')
summary(m)
```

Accuracy was lower for the semantic task than for the perceptual task ($\beta$=`r round(coef(summary(m))[3,1], 2)`, SE=`r round(coef(summary(m))[3,2], 2)`, p=`r round(coef(summary(m))[3,4], 3)`) 
and for sentence stimuli compared to picture stimuli  ($\beta$=`r round(coef(summary(m))[2,1], 2)`, SE=`r round(coef(summary(m))[2,2], 2)`, p=`r round(coef(summary(m))[2,4], 3)`), 
with an interaction between stimulus type and task ($\beta$=`r round(coef(summary(m))[4,1], 2)`, SE=`r round(coef(summary(m))[4,2], 2)`, p=`r round(coef(summary(m))[4,4], 3)`). 

```{r acc plot, echo=FALSE}
ggplot(data=dat_acc)+
    stat_summary(mapping = aes(x = Condition, y = Accuracy), 
               geom = 'col', fun.y = 'mean', color = 'gray',
               show.legend=FALSE)+
    stat_summary(mapping = aes(x = Condition, y = Accuracy), 
               geom = 'errorbar', fun.data = 'mean_se', color = 'black', 
               size = 1, width=0.3) + theme_minimal()
```